Volatility and the Buyback Anomaly: Interactive Tool

### 2017-02-17 manuscript.Rnw
files

source("../FinanceLibraries/lib_helpers.R", chdir=TRUE)
source("../FinanceLibraries/latex_code.R")
source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
source("Paper_global_parameters.R")

>>>>

source("library_files/lib_helpers.R", chdir=TRUE)
source("library_files/latex_code.R")
source("library_files/ff_industries_sic.R")
source("Paper_global_parameters.R")
